The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Tr\"aff and Francesco Versaci, ``Parallel Algorithms'' lecture, 2012 winter term at TU Wien.}

### 2014-03-18 article/article.tex
use inline enumeration for 2 short requirements

The following constraints have to be fulfilled by a witness tree. 
\begin{enumerate}
\item The ball $b_r$ that is represented by the root node $r$ has to exist at time step $t$. 
\item Each ball $b_v$ represented by a node $v \neq r$ with parent node $u$ has to exist when the ball $b_u$ is inserted.
\end{enumerate}
We say that an edge or leaf event is activated if the associated event occurs. A witness tree is activated when all its edge and leaf events are activated.

>>>>

The following constraints have to be fulfilled by a witness tree:
\begin{inparaenum}[(i)]
\item The ball $b_r$ that is represented by the root node $r$ has to exist at time step $t$ and 
\item each ball $b_v$ represented by a node $v \neq r$ with parent node $u$ has to exist when the ball $b_u$ is inserted.
\end{inparaenum}
We say that an edge or leaf event is activated if the associated event occurs. A witness tree is activated when all its edge and leaf events are activated.
